prep_annotating

### 2022-06-23 code/prep_annotate.Rmd
sample for inter-annotator agreement

```{r}
d.rounds.final %>% filter(game_complete) %>% 
  group_by(gameId) %>% summarise(utils=sum(playerUtility)) %>% arrange(desc(utils))

@@

good_chat <- d.raw_chat.final %>% 
  left_join(d.players %>% select(playerId, name)) %>% 
  rename(roundId=roundID) %>% 
  left_join(good_contexts) %>% 
  left_join(good_rounds) %>% 
  mutate(rowid=row_number(),
         span="",
         referent="",) %>% 
  select(rowid,trialNum,name, pResp, text,span, referent, flowers, color) %>% 
  filter(!is.na(text)) %>% 
  write_tsv(here(annotation_path, "pre_annotation.tsv"))

>>>>

```{r}
d.rounds.final %>% filter(game_complete) %>% filter(chatEnabled) %>% 
  group_by(gameId, conditionName,condition, ) %>% summarise(utils=sum(playerUtility)) %>% arrange(desc(utils))

@@

good_chat <- d.raw_chat.final %>% 
  left_join(d.players %>% select(playerId, name)) %>% 
  rename(roundId=roundID) %>% 
  left_join(good_contexts) %>% 
  left_join(good_rounds) %>% 
  mutate(rowid=row_number(),
         span="",
         referent="",) %>% 
  select(gameId,rowid,trialNum,name, pResp, text,span, referent, flowers, color) %>% 
  filter(!is.na(text)) %>% 
  write_tsv(here(annotation_path, "pre_annotation.tsv"))

```
# Choose games for agreement coding

```{r}
agreement_sample <- good_chat %>% filter(gameId %in% c("Rq47E8uzWFKm4CBPJ","Etbyk29DvPTqmSJM7")) %>% write_tsv(here(annotation_path, "pre_agreement.tsv"))
```
